Model LF

### 2022-10-31 Estimation.Rmd
Commit

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1) + L(log(mean_dp_regul),1) + d_2007q4)

@@

```{r}
g_yk_ds= TSDELTALOG(yk_ds)
g_prod_ds= TSDELTALOG(prodk_ds)

test_reg= dynlm(g_prod_ds ~ 1 + g_yk_ds + L(g_yk_ds,1) + L(g_prod_ds,1))
summary(test_reg)

>>>>

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1) + L(log(mean_dp_regul),1) + d_2007q4)

### Prod 1

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),1:4) +  L(TSDELTA(s_h),0:4)+  L(TSDELTALOG(mean_dp_regul),0:4) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(s_h,1)+ L(log(mean_dp_regul),1))

 prod_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 1:4)", c(3))
 s_h_vars_1 <- str_c("L(TSDELTA(s_h), 0:4)", c(0:2,4))
 dp_person_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(0:2,4))
  y_ds_vars_1 <- str_c("L(TSDELTALOG(y_ds), 0:4)", c(2,3,4))

vars_out_1 <- c( prod_vars_1,s_h_vars_1,dp_person_vars_1 ,y_ds_vars_1)
vars_out_1

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(prod_ds),c(1,4))  +  L(TSDELTALOG(y_ds),0:1) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(s_h,1)+ L(log(mean_dp_regul),1))

@@

```{r}
g_yk_ds= TSDELTALOG(yk_ds)
g_prodk_ds= TSDELTALOG(prodk_ds)

test_reg= dynlm(g_prodk_ds ~ 1 + g_yk_ds + L(g_yk_ds,1) + L(g_prodk_ds,1))
summary(test_reg)
